---
title: "244 Lab 4"
author: "Molly Williams"
date: "1/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


0. Load Packages
```{r}

library(tidyverse)
library(Ecdat) #there's data within packages!
library(plm)
library(lmtest)
library(car)
```


1. Part 1: Nonlinear least squares (logistic growth of bacteria)

```{r}

CellGrowth <- read_csv("CellGrowth.csv")

# Look at it:

ggplot(CellGrowth, aes(x = Time, y = CellCount)) + 
  geom_point()

# Estimate for K: 3700? Have to provide initial estimates for the model for convergence

## Find estimates for logistic growth:
## N = A/(1+Be^(~rt))
## Predictor variable = time, outcome variable = population size 
## 2100 = reasonable estimate for population starting size (N0) - if this is true, what is B?

BEstimate <- (3700 - 2000)/2000 # ~0.85

# Look back at the graph to see where exponential growth is happening; appox 0-5
## Estimate r (the growth rate)

lag_phase <- CellGrowth %>% 
  filter(Time<5)

ggplot(lag_phase, aes(x = Time, y = log(CellCount))) +
  geom_point()

# Since slope looks linear on log scale, you know this was a good estimate of the exponential growth phase 

lm(log(CellCount) ~ Time, data = lag_phase)

# Spits out a time estimate of 0.1035

```

Find model A, B, and r using Gauss-Newton method for iterative convergence (nonlinear least squares)
 
Use the nls() function:

```{r}

cell_fit <- nls(CellCount ~ A/(1+B*exp(-r*Time)),
                start = list(A = 3700, B = 0.85, r = 0.1035),
                data = CellGrowth,
                trace = TRUE)

# Returns a traceback of all iterations

cell_fit

A <- coef(cell_fit)[1] # don't set to an exact number in case something in the data changes; this way automatically updates if the model is updated
B <- coef(cell_fit)[2]
r <- coef(cell_fit)[3]

# Now everything is stored in a way that will allow you to plot them! 

# Create a new sequence of time values (time_seq)
time_seq <- seq(0,20, length = 100) # Creates string of new values between 0 and 20; default is increments of one, so adding length = 100 says how many values are wanted 

# Plug the new sequence into the model with the parameters A, B and r that we found:

cell_pred <- A/(1+B*exp(-r*time_seq))

pred_df <- data.frame(time_seq, cell_pred)

ggplot(CellGrowth, aes(x = Time, y = CellCount)) + 
  geom_point(colour = "blue", size = 3) + 
  theme_bw() +
  geom_line(data = pred_df, aes(x = time_seq, y = cell_pred), colour = "orange", size = 1) + 
  xlab("Time (h)") +
  ylab("Cell Count") +
  ggtitle("Bacterial Growth")
```


2. Panel Regression: First shot


Entities variable: states
Time variable: year
Dependent variable: packpc
avgprs: out predictor variable of interest


*What is the effect of cigarette price on purchases?*

```{r}

cigs_panel <- Cigarette %>% 
  select(state, year, packpc, avgprs) #only retaining the 4 columns we're interested in


# What is the relationship overall if we look at data by state?

ggplot(cigs_panel, aes(x = avgprs, y = packpc, group = state)) + 
  geom_point(aes(color = state)) + 
  geom_smooth(method = "lm", aes(color = state, se = FALSE, size = 0.3)) # whyyy are these lines so fat??

ggplot(cigs_panel, aes(x = year, y = packpc, group = state)) + 
  geom_point(aes(color= state)) +
  geom_smooth(method = "lm", aes(color = state), se = FALSE, size = 0.2)
```

Entity fixed effects model:

```{r}

cigs_model <- plm(packpc ~ avgprs,
                  data = cigs_panel,
                  index = c("state", "year"),
                  model = "within")

cigs_model

coeftest(cigs_model, vcov. = vcovHC(cigs_model, type = "HC1"))


```

Add time fixed effects:

```{r}

et_cigs_model <- plm(packpc ~ avgprs,
                     data = cigs_panel,
                     index = c("state", "year"),
                     model = "within",
                     effect = "twoways")


et_cigs_model

coeftest(et_cigs_model, vcov. = vcovHC(et_cigs_model, type = "HC1")) #coefficient is still highly significant, but is a different value

# Which model is better? Should we use time fixed effects, or just entity fixed effects?

pFtest(et_cigs_model, cigs_model)


```

**Conclusion:** Yes, we should include time fixed effects.  This makes sense, because we know that cigarette use is decreasing universally over time due to so many factors - health, societal pressure, etc.  We would expect time to substantially influence the number of packs per person.













